---
output: pdf_document
---

The following includes some exploratory data analysis on the Lobster orderbook data. For this analysis, we use the Google ticker set 10 price levels per orderbook.

```{r, echo=FALSE}
# Our filepaths ;)
# setwd("C:/Users/Amit/Documents/Github/reinforcement-learning-market-microstructure/data")
setwd("/Users/jacobkahn/Documents/University of Pennsylvania -- Penn/Co-Curriculars Clubs and Competitions/Wharton Investment and Trading Group - QIS Quant/Quant -- Reinforcement Learning Trading/reinforcement-learning-market-microstructure")

# Read in data
timeseries_raw = read.csv("data/10_GOOG.csv")
timeseries = data.frame(timeseries_raw)

# Add time interval stamps
timeseries$timestamp = seq.int(nrow(timeseries))

# Extract asks and bids
asks = timeseries[,1]
bids = timeseries[,3]

# Composite metrics
spread = asks - bids
ask_vols = timeseries$X100
bid_vols = timeseries$X496
vol_spread = ask_vols - bid_vols

```

We start by observing the overall state of the asset (Google class A shares). We plot the asks:
```{r}
# Plots
# Asks
plot(timeseries$timestamp, asks, "l")
```

Followed by the bids:
```{r, echo=FALSE}
# Bids
plot(timeseries$timestamp, bids, "l")
lines(timeseries$timestamp,bids, col="red")
```

The the price of the asset is in a clear state of decline over the course of the period. This market regime have several affets on the overall state of the algorithm and learning environment.


We continue with bid volumes:
```{r}
# Bid vols
plot(timeseries$timestamp, bid_vols, "l", col="blue")
```

And ask volumes:
```{r}
# Ask vols
plot(timeseries$timestamp, ask_vols, "l")
lines(timeseries$timestamp, ask_vols, col="red")
```

The volume on the spread:
```{r}
# Vol spread
plot(timeseries$timestamp, vol_spread, "l", col="blue")
```
